\section{Prompts Clasificacion}\label{sec:prompts}


\subsection{Base: 0-shot prompts}

\textbf{Prompt 0}: you are an English teacher and I want you to classify the following text according to the CEFR classes. I want you to respond only with the class (A1|B1|C1|A2|B2|C2). Without introduction.

\textbf{Prompt 1}: you are an English teacher and I want you to classify the following text for reading comprehension according to the CEFR classes. I want you to respond only with the class (A1|B1|C1|A2|B2|C2), without introduction.

\textbf{Prompt 2}: you are an English teacher and I want you to classify the following text according to the CEFR classes. I want you to respond only with the class (A1|B1|C1|A2|B2|C2). Without introduction.

\textbf{Prompt 3}: you are an English teacher and I want you to classify the following text for reading comprehension according to the CEFR classes. I want you to respond only with the class (A1|B1|C1|A2|B2|C2). without introduction.

\textbf{Prompt 4}:  Can you classify the following text according to its Common European Framework of Reference (CEFR) readibility level? I want you to respond only with the class (A1|A2|B1|B2|C1|C2). Without introduction.

\textbf{Prompt 5}: I'm a teacher of English who is preparing a reading task. Can you classify the following text regarding its readability based on the CEFR? I want you to respond only with the class (A1|A2|B1|B2|C1|C2). Without introduction.

\textbf{Prompt 6}: I'm a teacher of English as a foreign language. I'm preparing a reading task for my students and I would like to use the following text. Can you tell me which CEFR level is the following text suitable for? I want you to respond only with the class (A1|A2|B1|B2|C1|C2). Without introduction.

\textbf{Prompt 7}: I'm a teacher of English as a foreign language. I'm preparing a reading task for my students and I would like to use the following text. Can you classify the following text according to its CEFR readability level? I want you to respond only with the class (A1|A2|B1|B2|C1|C2). Without introduction.

\textbf{Prompt 8}: I'm a teacher of English as a foreign language. I'm preparing a reading task for my students and I would like to use the following text. Can you annotate the following text according to its CEFR readability level? I want you to respond only with the class (A1|A2|B1|B2|C1|C2). Without introduction.

\subsection{1-shot y 2-shot prompts}

\textbf{Prompt 9 (1 ejemplo por cada nivel + Prompt 0)}: this is an example of a text for level A1 $<Ejemplo>$\\
this is an example of a text for level B1  $<Ejemplo>$\\
this is an example of a text for level B2  $<Ejemplo>$\\
this is an example of a text for level C1 $<Ejemplo>$\\
this is an example of a text for level C2  $<Ejemplo>$\\
you are an English teacher and I want you to classify the following text according to the CEFR classes. I want you to responds only with the class (A1|A2|B1|B2|C1|C2). Without introduction.

\textbf{Prompt 10 (1 ejemplo por cada nivel + Prompt 1)}, tal como el Prompt 9.

\textbf{Prompt 11 (1 ejemplo por cada nivel + Prompt 2)}, tal como el Prompt 9.

\textbf{Prompt 12 (1 ejemplo por cada nivel + Prompt 3)}, tal como el Prompt 9.

\textbf{Prompt 13 (1 ejemplo por cada nivel salvo el nivel B2 + Prompt 0)}, tal como el Prompt 9.

\textbf{Prompt 14 (1 ejemplo por cada nivel salvo el nivel B2 + Prompt 1)}, tal como el Prompt 9.
2-shot prompts

\textbf{Prompt 15 (2 ejemplos por cada nivel + Prompt 0)}, tal como el Prompt 9.

\textbf{Prompt 16 (2 ejemplos por cada nivel + Prompt 1)}, tal como el Prompt 9.

\textbf{Prompt 17 (2 ejemplos por cada nivel + Prompt 2)}, tal como el Prompt 9.

\textbf{Prompt 18 (2 ejemplos por cada nivel + Prompt 2)}, tal como el Prompt 9.

\textbf{Prompt 19 (2 ejemplos por cada nivel salvo el nivel B2 + Prompt 0)}, tal como el Prompt 9.

\textbf{Prompt 20 (2 ejemplos por cada nivel salvo el nivel B2 + Prompt 1)}, tal como el Prompt 9.

\subsection{Prompts con conocimiento de dominio}

\textbf{Prompt 21}: this is a list of CEFR level descriptors for level A1: $<$Descriptores A1$>$\\
this is a list of CEFR level descriptors for level A2: $<$Descriptores A2$>$\\
this is a list of CEFR level descriptors for level B1: $<$Descriptores B1$>$\\
this is a list of CEFR level descriptors for level B2: $<$Descriptores B2$>$\\
this is a list of CEFR level descriptors for level C1: $<$Descriptores C1$>$\\
this is a list of CEFR level descriptors for level C2: $<$Descriptores C2$>$\\
Using the above descriptors I want you to classify the following text according to its Common European Framework of Reference (CEFR) level. I want you to responds only with the class (A1|A2|B1|B2|C1|C2). Without introduction.

\textbf{Prompt 22}: Igual al Prompt 21, sin los descriptores para el nivel B2

\textbf{Prompt 23}: This is a list of words sorted by levels A1, A2, B1, B2, C1, C2. In each level you will find words that a text of that level should have. In addition, the words of each higher level include the words of the lower level.\\
These are the words of level A1 $<$Vocabulario A1$>$\\
These are the words of level A2 $<$Vocabulario A2$>$\\
These are the words of level B1 $<$Vocabulario B1$>$\\
These are the words of level B2 $<$Vocabulario B2$>$\\
These are the words of level C1 and C2 $<$Vocabulario C1 y C2$>$\\
Using the above words, I want you to classify the following text according to its Common European Framework of Reference (CEFR) level. I want you to responds only with the class (A1|A2|B1|B2|C1|C2). Without introduction.